RDF Validation Requirements - Evaluation and Logical Underpinning

### 2014-12-26 paper/RDF validation requirements/RDF validation requirements.tex
added mapping tables

@@

\begin{ex}
# ShEx
# ----
<IssueShape> {
    :state (:unassigned :assigned),
    :reportedBy @<UserShape>,
    :related @<IssueShape>*
}
\end{ex}

@@

\begin{itemize}
	\item make sure that a value is valid for its datatype
\end{itemize}

@@

\begin{DL} 
$\rho(\textsf{hasBirthday}) \sqsubseteq \PVerb{xsd:dateTime}$\\
(equal to the definition of an attribute (data property) range)
\end{DL}

@@

@@

\begin{itemize}
	\item states that two different names are known to refer to the same individual \cite{Kroetzsch2012}
\end{itemize}

@@

\begin{gcotable}
class & \{julia\} & - & - & \{john\} & = \\
class & \{john\} & - & - & \{julia\} & = \\
\end{gcotable}

@@

@@

\begin{DL}
$\{julia\} \ne \{john\} $\\
(this is by default because of the UNA)
\end{DL}

\begin{itemize}
	\item asserts that Julia and John are actually different individuals
\end{itemize}

\begin{gcotable}
class & \{julia\} & - & - & \{john\} & $\ne$ \\
class & \{john\} & - & - & \{julia\} & $\ne$ \\
\end{gcotable}

>>>>

\begin{gcotable}
property & $\exists$ studentOf.JediMentor & studentOf & - & JediMentor & $\exists$ & - \\
class & JediMentor & - & - & $\exists$ studentOf.JediMentor & $\neg$ & - \\
\end{gcotable}

@@

\begin{ex}
# ShEx
# ----
<IssueShape> {
    :related @<IssueShape>*
}
\end{ex}

@@

Make sure that a value is valid for its datatype.

@@

@@

\begin{gcotable}
class & $\top$ & shoeSize & - & xsd:nonNegativeInteger & value valid for datatype & - \\
\end{gcotable}

\begin{DL} 
$\rho(\textsf{hasBirthday}) \sqsubseteq \PVerb{xsd:dateTime}$\\
\end{DL}

Equal to the definition of a data property range.

\tb{I do not understand the relation of this example to this constraint}

@@

\ms{Individual equality} states that two different names are known to refer to the same individual \cite{Kroetzsch2012}.

@@

\begin{gcotable}
class & \{julia\} & - & - & \{john\} & = & - \\
class & \{john\} & - & - & \{julia\} & = & - \\
\end{gcotable}

@@

This is by default because of the UNA.

@@

\begin{DL}
$\{julia\} \ne \{john\} $\\
\end{DL}

Asserts that Julia and John are actually different individuals.

\begin{gcotable}
class & \{julia\} & - & - & \{john\} & $\ne$ & - \\
class & \{john\} & - & - & \{julia\} & $\ne$ & - \\
\end{gcotable}
